Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
rewrite 3.1

\[
  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]
where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
Notice that $\betaset$ has $n+2$ elements, and the Bayesian Inference
process will produce an element from $\betaset$ that we denote by
$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
prior,  which from now on we consider fixed and we denote it by $\bprior$.

@@

 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--
 of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

\subsection{Analysis of the mechanism}
In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\betaset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
 $r\in\betaset$ we have:
$$
\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
 \hlg(\bysinfer(x),r)]\Big )
$$
To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

>>>>

\[
  \betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}
\]
where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
Notice that $\betaset$ has $n + 1$ elements, and the Bayesian Inference
process will produce an element from $\betaset$ that we denote by
$\bysinfer(\dataobs)$ -- we don't explicitely parametrize the result by the
prior,  which from now on we consider fixed and we denote it by $\bprior$.

@@

 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

\subsection{Analysis of the mechanism}
% In what follows, we will use a correspondence between the probability
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
%  $r\in\betaset$ and the probability 
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
%  $r\in\betaset$ we have:
% $$
% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]\Big )
% $$
% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

% In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

\begin{theorem}
The mechanism $\hexpmech$ is $(\epsilon,\delta)-$differential privacy by setting $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, deduced from the proof of privacy.
\end{theorem}

This mechanism also extends to Dirichlet distribution $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
\hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
\]
and replacing the $\betaset$ with set of Dirichlet distribution candidates of the same dimension under the same settings. Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements when extends to Dirichlet distribution.
